\chapter*{Список Литературы}
\addcontentsline{toc}{chapter}{Список Литературы}
\begin{enumerate}
    \item Humphry, D. The Bakerian Lecture. On some of the combinations of \\ oxymuriatic gas and oxygene, and on the chemical relations of these principles, to inflammable bodies / D. Humphry. -- Текст: непосредственный // \\ Phil. Trans. R. Soc. -- 1811. -- Vol. 101. -- P. 1-35.
    \item Faraday, M.  On fluid chlorine / M. Faraday. -- Текст: непосредственный // Phil. Trans. Roy. Soc. -- 1823. -- Vol. 113.-- P. 160-165.
    \item Roozeboom, H.W.B. Sur l'hydrate de l'acide sulfureux / H.W.B Roozeboom. -- Текст: непосредственный // Rec. Trav. Chem. Pays-Bas. -- 1884. -- Vol .3. -- P. 26.
    \item Villard, P. Sur quelques nouveaux hydrates de gaz / P. Villard. -- Текст: \\ непосредственный // Compt. Rend. -- 1888. -- Vol. 106. -- P. 1602-1603.
    \item de Forcrand, R. Sur la composition des hydrates de gaz / R. de Forcrand. -- Текст: непосредственный // Compt. Rend -- 1902. -- Vol. 135. -- P. 959.
    \item Hammerschmidt, E.G. Formation of Gas Hydrates in Natural Gas \\ Transmission Lines / E.G. Hammerschmidt. -- Текст: непосредственный // Ind. Eng. Chem. -- 1934. -- Vol. 26. -- № 8. -- P. 851-855.
    \item von Stackelberg, M. Zur Struktur der Gashydrate / M. von Stackelberg, H.R. Muller. -- Текст: непосредственный // Naturwiss. -- 1951.-- Vol. 38.-- P. 456.
    \item von Stackelberg, M. Feste Gashydrate II: Struktur und Raumchemie / M. von Stackelberg, H.R. Muller. -- Текст: непосредственный // Zeitschrift für Elektrochemie. -- 1954. -- Vol. 58. -- № 1. -- P. 25-39.
    \item Claussen, W. F. Solubilities and Structures in Aqueous Aliphatic Hydrocarbon Solutions / W. F. Claussen, M. F. Polglase.. -- Текст: непосредственный // J. Am. Chem. Soc. -- 1952. -- Vol. 74. -- № 19. -- P. 4817--4819.
    \item A new clathrate hydrate structure / J. A. Ripmeester, J. S. Tse, C. I. Ratcliffe, B. M. Powell. -- Текст: непосредственный // Nature. -- 1987. -- Vol. 325. -- № 6100. -- P. 135-136.
    \item Dyadin Y.A. Decomposition of methane hydrates up to 15 kbar / Y.A. Dyadin, E.Y. Aladko, E.G.Larionov. -- Текст: непосредственный // Mendeleev \\ Communications. -- 1997. -- Vol. 7. -- № 1. -- P. 34-35.
    \item J. H. van der Waals. Clathrate Solutions / J. H. van der Waals, J. C. Platteeuw. -- Текст: непосредственный // Adv. Chem. Phys. -- 1958. -- Vol. 2. -- P. 1-57.
    \item Cage Occupancy and Compressibility of Deuterated N2-Clathrate Hydrate by Neutron Diffraction / W.F. Kuhs, B. Chazallon, P.G. Radaelli, F. Pauer .-- Текст: непосредственный // Journal of inclusion phenomena and molecular recognition in chemistry. -- 1997. -- Vol. 29. -- P. 65-77.
    \item Gas hydrates in sustainable chemistry	/ A. Hassanpouryouzband, E. Joonaki, M. V. Farahani, S. Takeya [et. al]. -- Текст: непосредственный // Chem. Soc. Rev. -- 2020. -- Vol. 49. -- P. 5225.
    \item Durham, W.B. Ductile flow of methane hydrate /  W.B. Durham, L.A. Stern, S. H. Kirby. -- Текст: непосредственный // Canadian Journal of Physics . -- 2003. -- Vol. 81. -- №1. -- P. 373-380. 
    \item Davidson, D. W. Xenon-129 NMR and the thermodynamic parameters of xenon hydrate / D. W. Davidson, Y. P. Handa, J. A. Ripmeester. -- Текст: непосредственный // J. Phys. Chem. -- 1986. -- Vol. 90. -- № 24. -- P. 6549-6552.
    \item Waite, F. Thermal property measurements in Tetrahydrofuran (THF) hydrate and hydrate-bearing sediment between -25 and +4°C, and their application to methane hydrate William / F. Waite, L.Y. Gilbert, William J. Winters, David H. Mason. -- Текст: непосредственный // Gas hydrates: materials from 5th International Conference, (June 13-16 of 2005). -- Trondheim, Norway, 2005. -- P. 252-259.
    \item Kea, W. A review of gas hydrate nucleation theories and growth models / W. Kea, T. M. Svartaasb, D. Chena. -- Текст: непосредственный // Journal of Natural Gas Science and Engineering. -- 2019. -- Vol. 61. -- P. 169-196.
    \item Guo, G. Open questions on methane hydrate nucleation / G. Guo, Z. Zhang. -- Текст: непосредственный. // Communications Chemistry. -- 2021. -- Vol. 4, № 102.
    \item Mullin, J. W. Crystallization: учебное пособие / J. W. Mullin. -- Oxford: Изд-во Butterworth-Heinemann, 2001. -- Текст: непосредственный.
    \item Jacobson, L. C. Amorphous Precursors in the Nucleation of Clathrate Hydrates / L. C. Jacobson, W. Hujo, V. Molinero. -- Текст: непосредственный // J. Am. Chem. Soc. --  2010. -- Vol. 132. -- № 33. -- P. 11806–11811.
    \item Verlet, L. Computer "Experiments" on Classical Fluids. I. Thermodynamical Properties of Lennard-Jones Molecules / L. Verlet. -- Текст: непосредственный // Phys. Rev. -- Vol. 159. -- № 1. -- P. 98-103.
    \item Molinero, V. Water Modeled As an Intermediate Element between Carbon and Silicon / V. Molinero, E. B. Moore. -- Текст: непосредственный // J. Phys. Chem. B. -- 2009. -- Vol. 113. -- № 13. -- P. 4008 - 4016.
    \item Berendsen, H. J. C. Interaction models of water in relation to protein hydration / H. J. C. Berendsen, J. P. M. Postma, W. F. van Gunsteren, J. Hermans. -- Текст:непосредственный // Intermolecular forces: Proceedings of the \\ Fourteenth Jerusalem Symposium on Quantum Chemistry and Biochemistry, (April 13-16 of 1981). -- Jerusalem, Israel, 1981. -- P. 331-342.
    \item Comparison of simple potential functions for simulating liquid water / W. L. Jorgensen, J. Chandrasekhar, J. D. Madura, R. W. Impey [et al.]. -- Текст: непосредственный // J. Chem. Phys. -- 1983. -- Vol. 49. -- № 2. -- P. 926.
    \item Mahoney, M. W. A five-site model for liquid water and the reproduction of the density anomaly by rigid, nonpolarizable potential functions / M. W. Mahoney, W. L. Jorgensen. -- Текст:непосредственный // J. Chem. Phys. -- 2000. -- Vol. 112. -- P. 8910-8922.
    \item Simple water models. -- Изображение // Wikipedia. The free encyclopedia: [сайт]. -- URL: \url{https://en.wikipedia.org/wiki/Water_model#/media/} \\ \url{File:Water_models.svg} (Дата обращения 25.05.2022).
    \item Abascal, J. L. F. A potential model for the study of ices and amorphous water: TIP4P/Ice / J. L. F. Abascal, E. Sanz, R. García Fernández, C. Vega. -- Текст: непосредственный // J. Chem. Phys. -- Vol. 122. -- № 23. -- P. 234511.
    \item Four site water model. -- Изображение // SklogWiki: [сайт]. -- URL: \url{https://en.wikipedia.org/wiki/Water_model#/media/File:Water_models.svg} (Дата обращения 25.05.2022).
    \item Jorgensen, W. L. Optimized intermolecular potential functions for liquid hydrocarbons / W. L. Jorgensen, J. D. Madura, C. J. Swenson. -- Текст: непосредственный // J. Am. Chem. Soc. --  1984. -- Vol. 106. -- № 22. -- P. 6638–6646.
    \item Lorentz, H. A. Ueber die Anwendung des Satzes vom Virial in der kinetischen Theorie der Gase / H. A. Lorentz .-- Текст: непосредственный // Annalen der Physik. -- 1881. -- Vol. 248. -- № 1. -- P. 127-136.
    \item Berthelot, D. Sur le mélange des gaz / D. Berthelot. -- Текст: непосредственный // Comptes rendus hebdomadaires des séances de l’Académie \\ des Sciences. --  1898. Vol. -- 126. P. 1703-1855.
    \item Sveinsson, H. A. Molecular modeling of fracture in methane
    hydrates: Thesis for the degree of Master of Science / Henrik Andersen Sveinsson. -- Oslo, 2015. -- P. 64. -- Изображение.
    \item Jacobson, L. C. A Methane−Water Model for Coarse-Grained Simulations of Solutions and Clathrate Hydrates / L. C. Jacobson, V. Molinero. -- Текст: непосредственный // J. Phys. Chem. B. -- 2010. -- Vol. 114. -- № 21. -- P. 7302–7311.
    \item Stillinger, S.H. Computer simulation of local order in condensed phases of silicon / F. H. Stillinger, T. A. Weber // Phys. Rev. B. -- 1985. -- Vol. 31. -- № 8. -- P. 5262.
    \item Jacobson, L. C. Thermodynamic Stability and Growth of Guest-Free Clathrate Hydrates: A Low Density Crystal Phase of Water / L. C. Jacobson, W. Hujo, V. Molinero. -- Текст: непосредственный // J. Phys. Chem. B. -- 2009. -- Vol. 113. -- № 30. -- P. 10298-10307.
    10298-10307.
    \item Baez, L. A. Computer Simulation of the Crystal Growth and Dissolution of Natural Gas Hydrates / L. A. Baez, P. Clancy. -- Текст: непосредственный // Ann. N. Y. Acad. Sci. -- 1994. -- Vol. 715. --  № 1. -- P. 177-186.
    \item Nguyen, A. H. Identification of Clathrate Hydrates, Hexagonal Ice, Cubic Ice, and Liquid Water in Simulations: the CHILL+ Algorithm / A. H. Nguyen, V. Molinero. -- Текст: непосредственный // J. Phys. Chem. B. -- 2015. -- Vol. 119. -- № 29. -- P. 9369-9376.
    \item Steinhardt, P. J. Bond-orientational order in liquids and glasses / P. J. Steinhardt, D. R. Nelson, M. Ronchetti. -- Текст: непосредственный // Phys. Rev. B. -- 1983. -- Vol. 28. -- № 2. -- P. 784.
    \item ten Wolde, P. R. Numerical calculation of the rate of crystal nucleation in a Lennard‐Jones system at moderate undercooling / P.R. ten Wolde, M. J. Ruiz‐Montero, D. Frenkel. -- Текст: непосредственный // J. Chem. Phys. -- 1996. -- Vol. 104. -- № 24. -- P. 9932.
    \item Water proton configurations in structures I, II, and H clathrate hydrate unit cells / F. Takeuchi, M. Hiratsuka, R. Ohmura, S. Alavi [et al.]. -- Текст:непосредственный // J. Chem. Phys. -- 2013. -- Vol. 138. -- № 12. -- P. 124504.
    \item LAMMPS - a flexible simulation tool for particle-based materials modeling at the atomic, meso, and continuum scales / A. P. Thompson, H. M. Aktulga, R. Berger, D. S. Bolintineanu. -- Текст:непосредственный // Comp. Phys. Comm. -- 2022. -- Vol. 271. -- № 4. -- P. 10817.
    \item Stukowski, A. Visualization and analysis of atomistic simulation data with OVITO-the Open Visualization Tool / A. Stukowski. -- Текст:непосредственный // Modelling Simul. Mater. Sci. Eng. -- 2010. -- Vol. 18. -- № 1. -- P. 015012

\end{enumerate}